---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = NULL
)
```

# isopleuros

<!-- badges: start -->
[![R-CMD-check](https://github.com/tesselle/isopleuros/workflows/R-CMD-check/badge.svg)](https://github.com/tesselle/isopleuros/actions)
[![codecov](https://codecov.io/gh/tesselle/isopleuros/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tesselle/isopleuros)
[![CodeFactor](https://www.codefactor.io/repository/github/tesselle/isopleuros/badge/main)](https://www.codefactor.io/repository/github/tesselle/isopleuros/overview/main)

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

## Overview

Ternary plots made simple. **isopleuros** allows to create ternary plot using **graphics**. It provides functions to display the data in the ternary space, to add or tune graphical elements and to display statistical summaries. It also includes common ternary diagrams useful for the archaeologist (e.g. soil texture charts, ceramic phase diagram).

**isopleuros** is a dependency-free package designed to be as simple as possible. If you need finer tuning or more advanced features, you should consider the [**Ternary**](https://ms609.github.io/Ternary/) or [**ggtern**](http://www.ggtern.com/) package.

## Installation

You can install the released version of **isopleuros** from [CRAN](https://CRAN.R-project.org) with:

```{r cran-installation, eval=FALSE}
install.packages("isopleuros")
```

And the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/isopleuros")
```

## Usage

```{r packages-load}
## Install extra packages (if needed)
# install.packages("folio")

## Load packages
library(folio) # Datasets
library(isopleuros)
```

**isopleuros** tries to mimic the way **graphics** works as much as possible. This means that you should not be confused if you are familiar with the standard R graphics environment.

```{r ternary, fig.width=7, fig.height=7, fig.align='center'}
## Data from Barrera and Velde 1989
data("verre", package = "folio")

## Select data
coda <- verre[, c("Na2O", "CaO", "K2O")]

## Ternary plot
ternary_plot(coda, panel.first = ternary_grid())

## Split data
groups <- split(coda, f = coda$Na2O > 5)

## Add tolerance ellipses
for (group in groups) {
  ternary_tolerance(group, level = 0.95, border = "blue", lty = 2)
}
```

## Contributing

Please note that the **isopleuros** project is released with a [Contributor Code of Conduct](https://www.tesselle.org/conduct.html). By contributing to this project, you agree to abide by its terms.
